\bf What is the Best Way to Display Two Time Series to Read Association?

### 2016-02-09 paper/paper.Rnw
editing

\begin{figure}[htbp]
  \centering
    \begin{subfigure}[htbp]{0.45\textwidth}
    <<nzd, error=FALSE, message=FALSE, warning=FALSE, echo=FALSE>>=
    library(dplyr)
    library(tidyr)
    library(ggplot2)
    rates <- select(read.csv("data/rates.csv"), date, AUD, CNY, NZD)[36:69,]
    rates <- mutate(rates, AUD2=(AUD-mean(AUD))/sd(AUD), CNY2=(CNY-mean(CNY))/sd(CNY)) #scaling
    ggplot(data=rates, aes(x=AUD, y=NZD)) + geom_point()
    @
    \end{subfigure}
    \begin{subfigure}[htbp]{0.45\textwidth}
    <<nzd2, dependson='nzd', error=FALSE, message=FALSE, warning=FALSE, echo=FALSE>>=
    rates_l <- gather(rates, currency, value, -date)
    ggplot(data=subset(rates_l, currency != "CNY" & currency != "CNY2" & currency != "AUD2"), aes(x=as.Date(date), y=value, colour=currency)) + geom_line() + theme(legend.position="bottom")
    @
    \end{subfigure}
  \caption{Cross-rates for Australian and NZ dollars against US dollar, from Mar 30-May 2, 2015, shown using a scatterplot (left) and overlaid line graph (right). From which plot is correlation more accurately read? Point-wise correlation between the two series, ignoring autodependence, is 0.64.}
  \label{nzd}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \begin{subfigure}[t]{0.24\textwidth}
\subcaption{}\label{smootha}
<<smoothing, dependson='setup', fig.width=4, fig.height=4, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
set.seed(123)
uns <- gen_true_data(96, 0.8)
uns_l <- gather(uns, variable, value, -t)
set.seed(123)
sm <- gen_true_data(96, 0.8, smoothed = TRUE)
sm_l <- gather(sm, variable, value, -t)
ggplot(data=uns_l, aes(x=t, y=value, colour=variable)) + geom_line() + theme(aspect.ratio=1, axis.title.x = element_blank(), axis.title.y = element_blank(),
          axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank(), legend.position="none")
@
\end{subfigure}
\begin{subfigure}[t]{0.24\textwidth}
\subcaption{}\label{smoothb}
<<smoothing2, dependson='smoothing', fig.width=4, fig.height=4, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
ggplot(data=uns, aes(x=X1, y=X2)) + geom_point() + theme(aspect.ratio=1, axis.title.x = element_blank(), axis.title.y = element_blank(),
          axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank(), legend.position="none")
@
\end{subfigure}
\begin{subfigure}[t]{0.24\textwidth}
\subcaption{}\label{smoothc}
<<smoothing3, dependson='smoothing', fig.width=4, fig.height=4, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
ggplot(data=sm_l, aes(x=t, y=value, colour=variable)) + geom_line() + theme(aspect.ratio=1, axis.title.x = element_blank(), axis.title.y = element_blank(),
          axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank(), legend.position="none")
@
\end{subfigure}
\begin{subfigure}[t]{0.24\textwidth}
\subcaption{}\label{smoothd}
<<smoothing4, dependson='smoothing', fig.width=4, fig.height=4, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
ggplot(data=sm, aes(x=X1, y=X2)) + geom_point() + theme(aspect.ratio=1, axis.title.x = element_blank(), axis.title.y = element_blank(),
          axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank(), legend.position="none")
@
\end{subfigure}
  \caption{Plots illustrating the experimental design. The same AR(1) data both unsmoothed (\subref{smootha} and \subref{smoothb}) and smoothed (\subref{smoothc} and \subref{smoothd}) for both plot designs, with t = 96 and correlation = 0.86}
  \label{smoothing}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \begin{subfigure}[t]{0.24\textwidth}
\subcaption{}\label{designa}
<<designs, dependson='setup', fig.width=4, fig.height=4, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
set.seed(101)
a <- gen_true_data(24, 0.95)
b <- gen_true_data(24, -0.95)
a_l <- gather(a, variable, value, -t)
b_l <- gather(b, variable, value, -t)
ggplot(data=a_l, aes(x=t, y=value, colour=variable)) + geom_line() + theme(aspect.ratio=1, axis.title.x = element_blank(), axis.title.y = element_blank(),
          axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank(), legend.position="none")
@
\end{subfigure}
\begin{subfigure}[t]{0.24\textwidth}
\subcaption{}\label{designb}
<<designs2, dependson='designs', fig.width=4, fig.height=4, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
ggplot(data=b_l, aes(x=t, y=value, colour=variable)) + geom_line() + theme(aspect.ratio=1, axis.title.x = element_blank(), axis.title.y = element_blank(),
          axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank(), legend.position="none")
@
\end{subfigure}
\begin{subfigure}[t]{0.24\textwidth}
\subcaption{}\label{designc}
<<designs3, dependson='designs', fig.width=4, fig.height=4, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
ggplot(data=a, aes(x=X1, y=X2)) + geom_point() + theme(aspect.ratio=1, axis.title.x = element_blank(), axis.title.y = element_blank(),
          axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank(), legend.position="none")
@
\end{subfigure}
\begin{subfigure}[t]{0.24\textwidth}
\subcaption{}\label{designd}
<<designs4, dependson='designs', fig.width=4, fig.height=4, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
ggplot(data=b, aes(x=X1, y=X2)) + geom_point() + theme(aspect.ratio=1, axis.title.x = element_blank(), axis.title.y = element_blank(),
          axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank(), legend.position="none")
@
\end{subfigure}
\caption{Plots illustrating the experimental design: the two different plot types of the same data with $t=24$, $r= 0.946$ (\subref{designa} and \subref{designc}), $r= -0.943$ (\subref{designb} and \subref{designd}).}
\label{designs}
\end{figure}

>>>>

\begin{figure}[htbp]
  \centering
    \begin{subfigure}[htbp]{0.45\textwidth}
    <<nzd, error=FALSE, message=FALSE, warning=FALSE, echo=FALSE>>=
    rates <- select(read.csv("data/rates.csv"), date, AUD, CNY, NZD)[36:69,]
    rates <- mutate(rates, AUD2=(AUD-mean(AUD))/sd(AUD), CNY2=(CNY-mean(CNY))/sd(CNY)) #scaling
    ggplot(data=rates, aes(x=AUD, y=NZD)) + geom_point()
    @
    \end{subfigure}
    \begin{subfigure}[htbp]{0.45\textwidth}
    <<nzd2, dependson='nzd', error=FALSE, message=FALSE, warning=FALSE, echo=FALSE>>=
    rates_l <- gather(rates, currency, value, -date)
    ggplot(data=subset(rates_l, currency != "CNY" & currency != "CNY2" & currency != "AUD2"), aes(x=as.Date(date), y=value, colour=currency)) + geom_line() + theme(legend.position="bottom")
    @
    \end{subfigure}
  \caption{Cross-rates for Australian and NZ dollars against US dollar, from Mar 30-May 2, 2015, shown using a scatterplot (left) and overlaid line graph (right). From which plot is correlation more accurately read? Point-wise correlation between the two series, ignoring autodependence, is 0.64.}
  \label{nzd}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \begin{subfigure}[t]{0.24\textwidth}
\subcaption{}\label{smootha}
<<smoothing, dependson='setup', fig.width=4, fig.height=4, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
set.seed(123)
uns <- gen_true_data(96, 0.8)
uns_l <- gather(uns, variable, value, -t)
set.seed(123)
sm <- gen_true_data(96, 0.8, smoothed = TRUE)
sm_l <- gather(sm, variable, value, -t)
ggplot(data=uns_l, aes(x=t, y=value, colour=variable)) + geom_line() + theme(aspect.ratio=1, axis.title.x = element_blank(), axis.title.y = element_blank(),
          axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank(), legend.position="none")
@
\end{subfigure}
\begin{subfigure}[t]{0.24\textwidth}
\subcaption{}\label{smoothb}
<<smoothing2, dependson='smoothing', fig.width=4, fig.height=4, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
ggplot(data=uns, aes(x=X1, y=X2)) + geom_point() + theme(aspect.ratio=1, axis.title.x = element_blank(), axis.title.y = element_blank(),
          axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank(), legend.position="none")
@
\end{subfigure}
\begin{subfigure}[t]{0.24\textwidth}
\subcaption{}\label{smoothc}
<<smoothing3, dependson='smoothing', fig.width=4, fig.height=4, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
ggplot(data=sm_l, aes(x=t, y=value, colour=variable)) + geom_line() + theme(aspect.ratio=1, axis.title.x = element_blank(), axis.title.y = element_blank(),
          axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank(), legend.position="none")
@
\end{subfigure}
\begin{subfigure}[t]{0.24\textwidth}
\subcaption{}\label{smoothd}
<<smoothing4, dependson='smoothing', fig.width=4, fig.height=4, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
ggplot(data=sm, aes(x=X1, y=X2)) + geom_point() + theme(aspect.ratio=1, axis.title.x = element_blank(), axis.title.y = element_blank(),
          axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank(), legend.position="none")
@
\end{subfigure}
  \caption{Plots illustrating the experimental design. The same AR(1) data both unsmoothed (\subref{smootha} and \subref{smoothb}) and smoothed (\subref{smoothc} and \subref{smoothd}) for both plot designs, with t = 96 and correlation $\rho$ = 0.86}
  \label{smoothing}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \begin{subfigure}[t]{0.24\textwidth}
\subcaption{}\label{designa}
<<designs, dependson='setup', fig.width=4, fig.height=4, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
set.seed(101)
a <- gen_true_data(24, 0.95)
b <- gen_true_data(24, -0.95)
a_l <- gather(a, variable, value, -t)
b_l <- gather(b, variable, value, -t)
ggplot(data=a_l, aes(x=t, y=value, colour=variable)) + geom_line() + theme(aspect.ratio=1, axis.title.x = element_blank(), axis.title.y = element_blank(),
          axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank(), legend.position="none")
@
\end{subfigure}
\begin{subfigure}[t]{0.24\textwidth}
\subcaption{}\label{designb}
<<designs2, dependson='designs', fig.width=4, fig.height=4, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
ggplot(data=b_l, aes(x=t, y=value, colour=variable)) + geom_line() + theme(aspect.ratio=1, axis.title.x = element_blank(), axis.title.y = element_blank(),
          axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank(), legend.position="none")
@
\end{subfigure}
\begin{subfigure}[t]{0.24\textwidth}
\subcaption{}\label{designc}
<<designs3, dependson='designs', fig.width=4, fig.height=4, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
ggplot(data=a, aes(x=X1, y=X2)) + geom_point() + theme(aspect.ratio=1, axis.title.x = element_blank(), axis.title.y = element_blank(),
          axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank(), legend.position="none")
@
\end{subfigure}
\begin{subfigure}[t]{0.24\textwidth}
\subcaption{}\label{designd}
<<designs4, dependson='designs', fig.width=4, fig.height=4, out.width='0.9\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
ggplot(data=b, aes(x=X1, y=X2)) + geom_point() + theme(aspect.ratio=1, axis.title.x = element_blank(), axis.title.y = element_blank(),
          axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank(), legend.position="none")
@
\end{subfigure}
\caption{Plots illustrating the experimental design: the two different plot types of the same data with $t=24$, $\rho= 0.946$ (\subref{designa} and \subref{designc}), $\rho= -0.943$ (\subref{designb} and \subref{designd}).}
\label{designs}
\end{figure}
